---
title: "Who are the elected representatives?"
output:
  html_document: default
css: styles.css
---

```{r setup, include=FALSE}
## this is the code chunk for R setup.
## You may load libraries and your google key here
## You can also set various knitr options here
knitr::opts_chunk$set(echo=FALSE, message=FALSE)
library(httr)
library(jsonlite)
library(dplyr)
library(tidyr)
library(knitr)

source("~/Documents/keys.R") 
source('process-data.R')

```

In the following data, we share information regarding local elected officials by utilizing the [Google Civic Information API](https://developers.google.com/civic-information/). 
To make this work, first we input an address into our getReps function. 
The output of this function is a data table which contains the names of relevant local government leaders, their political party, office phone number, URL, photos, and office email.


The addresses we will be looking at are:
```{r}
address1 <- "7009 Sunset Blvd, Los Angeles, CA 90028"
                           
address2 <- "10107 W. 75th Street Overland Park, KS 66204"
                           
```
**`r address1`** and **`r address2`** 

# Elected officials for the first address

The **In-N-Out** restaurant in **Los Angeles, California** has these constituents in their local and national government:  

```{r}
tbl <- getReps(address1)
kable(tbl)

```

# Elected officials for the second address

The next location is a **Taco Bell** in the middle of **Kansas**. 
This location has these constituents in their local and national government: 

```{r}
tbl2 <- getReps(address2)
kable(tbl2)
```

